### 2020-04-14 prep.tex
prep update
include
Don't end document early
Make affiliations consistent
(and find missing ones)

\include{preface}

@@

	\subsection*{Programme committee}
	\begin{compactitem}[]
	\item[] Dale Hample, chair (University of Maryland)
	\item[] Henrike Jansen, secretary (University of Leiden)
	\item[] Marcin Lewinski (Universidade Nova de Lisboa)
	\item[] Frank Zenker (Universität Konstanz, Slovak Academy of Sciences, Lund University)
	\item[] Juho Ritola (University of Turku)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
	\item[] Fabio Paglieri, chair (ISTC-CNR, Rome, Italy)
	\item[] Jan Albert Van Laar, deputy chair (University of Groningen, The Netherlands)
	\item[] Lilian Bermejo Luque (University of Granada, Spain)
	\item[] Katarzyna Budzyńska (Polish Academy of Sciences, Poland)
	\item[] Henrike Jansen (University of Leiden, The Netherlands)
	\item[] Marcin Koszowy (University of Białystok, Poland)
	\item[] Marcin Lewiński (Universidade Nova de Lisboa, Portugal)
	\item[] Dima Mohammed (Universidade Nova de Lisboa, Portugal)
	\item[] Steve Oswald (University of Fribourg, Switzerland)
	\item[] Juho Ritola (University of Turku, Finland)
	\item[]Sara Rubinelli (University of Lucerne, Switzerland)
	\item[] Frank Zenker (University of Lund, Sweden)
	\end{compactitem}

@@

		\item[] Adam Richards
		\item[] Alessandra Von Burg, Wake Forest University
		\item[] Amy Johnson
		\item[] Andrea Rocci, Università della Svizzera Italiana
		\item[] Andrei Moldovan, University of Salamanca
		\item[] Andrew Aberdein, Florida Institute of Technology
		\item[] Assimakis Tseronis, Örebro University
		\item[] Bart Garssen, University of Amsterdam
		\item[] Bart van Klink, Vrije Universiteit Amsterdam
		\item[] Beth Innocenti, University of Kansas
		\item[] Carly Woods, University of Maryland
		\item[] Catherine Hundleby, University of Windsor
		\item[] Christoph Lumer, University of Siena
		\item[] Christopher Tindale, University of Windsor
		\item[] Constanza Ihnen, University of Chile, Law Faculty, Institute of Argumentation
		\item[] Corina Andone, University of Amsterdam
		\item[] Daniel Cohen
		\item[] David Godden, Michigan State University
		\item[] David Hitchcock, McMaster University
		\item[] David Williams, Florida Atlantic University
		\item[] David Zarefsky, Northwestern University
		\item[] Eveline Feteris, University of Amsterdam
		\item[] Fabrizio Macagno, Universidade NOVA de Lisboa
		\item[] Floriana Grasso, University of Liverpool
		\item[] Francisca Snoeck Henkemans, University of Amsterdam
		\item[] C. Goddu, University of Richmond
		\item[] Gabor Zemplen, Budapest University of Technology and Economics
		\item[] Gabrijela Kisicek, University of Zagreb
		\item[] Gilbert Plumer, Law School Admission Council (retired)
		\item[] Gregor Betz, KIT Karlsruhe
		\item[] Hans Hoeken, Utrecht University
		\item[] Hans Vilhelm Hansen, University of Windsor
		\item[] Harald Wohlrapp,
		\item[] Harry Weger, University of Central Florida
		\item[] Harvey Siegel, University of Miami
		\item[] Hen Jans, Univ Leiden
		\item[] Henry Prakken, Department of Information and Computing Sciences, University of Utrecht \& Faculty of Law, University of Groningen
		\item[] Igor Z. Zagar, Educational Research Institute
		\item[] Ingeborg van der Geest, University of Amsterdam
		\item[] Isabela Fairclough, University of Cantral Lancashire
		\item[] Anthony Blair, University of Windsor
		\item[] Jacky Visser, University of Dundee
		\item[] Jean Goodwin
		\item[] Jérôme Jacquin, University of Lausanne
		\item[] Joana Garmendia, ILCLI (University of the Basque Country)
		\item[] John Casey, Northeastern Illinois University
		\item[] Jos Hornikx, Radboud University
		\item[] Juho Ritola, University of Helsinki
		\item[] Katharina Stevens, University of Lethbridge
		\item[] Laura Vincze, Dpt of Linguistics, Pisa
		\item[] Lena Wahlberg, Lund University
		\item[] Leo Groarke, Trent University
		\item[] Lotte Van Poppel, University of Amsterdam
		\item[] Louis De Saussure, University of Neuchatel
		\item[] Maarten van Leeuwen, Leiden University Centre for Linguistics (LUCL)
		\item[] Manfred Kienpointner, University of Innsbruck
		\item[] Manfred Kraus, University of Tübingen
		\item[] Manfred Stede, Univ Potsdam
		\item[] Marianne Doury, Paris Descartes University
		\item[] Mariusz Urbanski, Adam Mickiewicz University
		\item[] Mark Aakhus, Rutgers University
		\item[] Marta Zampa, Zurich University of Applied Sciences
		\item[] Martin Hinton, University of Lodz
		\item[] Martin Reisigl, University of Bern
		\item[] Mehmet Ali Uzelgun, Universidade NOVA de Lisboa
		\item[] Michael Baumtrog, Ryerson University
		\item[] Michael Hoffmann, Georgia Institute of Technology
		\item[] Michael Hoppmann, Northeastern University
		\item[] Michel Dufour, Université Sorbonne-Nouvelle
		\item[] Minghui Xiong, Institute of Logic and Cognition, Sun Yat-sen University
		\item[] Niki Pfeifer, Munich Center for Mathematical Philosophy
		\item[] Patrick Bondy, Cornell University
		\item[] Paula Olmos,
		\item[] Rudi Palmieri, University of Liverpool
		\item[] Ruth Amossy, Tel-Aviv University
		\item[] Sara Greco, Università della Svizzera italiana
		\item[] Sarah Bigi, Università Cattolica del Sacro Cuore
		\item[] Scott Aikin, Vanderbilt University
		\item[] Steven Patterson, Marygrove College
		\item[] Susan Kline, The Ohio State University
		\item[] Thierry Herman, Universities of Neuchatel and lausanne
		\item[] Yun Xie, Sun Yat-sen Univ.

@@

% \newpage
% \pdfbookmark[chapter]{Table of Contents}{toc}
% \tableofcontents
% \newpage

 \pdfbookmark[chapter]{Preface}{preface}

\mainmatter
\MakePlainPagestyleEmpty

% \include{papers-with-names}

\backmatter

% \addcontentsline{toc}{chapter}{Index of Authors}
% \printindex[authors]

% \includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/back}

\end{document}

>>>>

@@

	\subsection*{Programme committee}
	\begin{compactitem}[]
		\item[] Dale Hample, chair (University of Maryland)
		\item[] Henrike Jansen, secretary (University of Leiden)
		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
		\item[] Frank Zenker (Lund University)
		\item[] Juho Ritola (University of Turku)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
		\item[] Fabio Paglieri, chair (ISTC-CNR)
		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
		\item[] Lilian Bermejo Luque (University of Granada)
		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
		\item[] Henrike Jansen (University of Leiden)
		\item[] Marcin Koszowy (University of Białystok)
		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
		\item[] Dima Mohammed (Universidade Nova de Lisboa)
		\item[] Steve Oswald (University of Fribourg)
		\item[] Juho Ritola (University of Turku)
		\item[]Sara Rubinelli (University of Lucerne)
		\item[] Frank Zenker (University of Lund)
	\end{compactitem}

@@

		\item[] Adam Richards (Texas Christian University)
		\item[] Alessandra Von Burg (Wake Forest University)
		\item[] Amy Johnson (University of Oklahoma)
		\item[] Andrea Rocci (Università della Svizzera Italiana)
		\item[] Andrei Moldovan (University of Salamanca)
		\item[] Andrew Aberdein (Florida Institute of Technology)
		\item[] Assimakis Tseronis (Örebro University)
		\item[] Bart Garssen (University of Amsterdam)
		\item[] Bart van Klink (Vrije Universiteit Amsterdam)
		\item[] Beth Innocenti (University of Kansas)
		\item[] Carly Woods (University of Maryland)
		\item[] Catherine Hundleby (University of Windsor)
		\item[] Christoph Lumer (University of Siena)
		\item[] Christopher Tindale (University of Windsor)
		\item[] Constanza Ihnen (University of Chile, Law Faculty, Institute of Argumentation)
		\item[] Corina Andone (University of Amsterdam)
		\item[] Daniel Cohen (Colby College)
		\item[] David Godden (Michigan State University)
		\item[] David Hitchcock (McMaster University)
		\item[] David Williams (Florida Atlantic University)
		\item[] David Zarefsky (Northwestern University)
		\item[] Eveline Feteris (University of Amsterdam)
		\item[] Fabrizio Macagno (Universidade NOVA de Lisboa)
		\item[] Floriana Grasso (University of Liverpool)
		\item[] Francisca Snoeck Henkemans (University of Amsterdam)
		\item[] C. Goddu (University of Richmond)
		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
		\item[] Gabrijela Kisicek (University of Zagreb)
		\item[] Gilbert Plumer (Law School Admission Council) (retired)
		\item[] Gregor Betz (KIT Karlsruher)
		\item[] Hans Hoeken (Utrecht University)
		\item[] Hans Vilhelm Hansen (University of Windsor)
		\item[] Harald Wohlrapp (Universität Hamburg)
		\item[] Harry Weger (University of Central Florida)
		\item[] Harvey Siegel (University of Miami)
		\item[] Hen Jans (University of Leiden)
		\item[] Henry Prakken (University of Groningen)
		\item[] Igor Z. Zagar (Educational Research Institute)
		\item[] Ingeborg van der Geest (University of Amsterdam)
		\item[] Isabela Fairclough (University of Cantral Lancashire)
		\item[] Anthony Blair (University of Windsor)
		\item[] Jacky Visser (University of Dundee)
		\item[] Jean Goodwin (North Carolina State University)
		\item[] Jérôme Jacquin (University of Lausanne)
		\item[] Joana Garmendia (University of the Basque Country)
		\item[] John Casey (Northeastern Illinois University)
		\item[] Jos Hornikx (Radboud University)
		\item[] Juho Ritola (University of Helsinki)
		\item[] Katharina Stevens (University of Lethbridge)
		\item[] Laura Vincze (Universityt of Pisa)
		\item[] Lena Wahlberg (Lund University)
		\item[] Leo Groarke (Trent University)
		\item[] Lotte Van Poppel (University of Amsterdam)
		\item[] Louis De Saussure (University of Neuchatel)
		\item[] Maarten van Leeuwen (Leiden University Centre for Linguistics) (LUCL)
		\item[] Manfred Kienpointner (University of Innsbruck)
		\item[] Manfred Kraus (University of Tübingen)
		\item[] Manfred Stede (University of Potsdam)
		\item[] Marianne Doury (Paris Descartes University)
		\item[] Mariusz Urbanski (Adam Mickiewicz University)
		\item[] Mark Aakhus (Rutgers University)
		\item[] Marta Zampa (Zurich University of Applied Sciences)
		\item[] Martin Hinton (University of Lodz)
		\item[] Martin Reisigl (University of Bern)
		\item[] Mehmet Ali Uzelgun (Universidade NOVA de Lisboa)
		\item[] Michael Baumtrog (Ryerson University)
		\item[] Michael Hoffmann (Georgia Institute of Technology)
		\item[] Michael Hoppmann (Northeastern University)
		\item[] Michel Dufour (Université Sorbonne-Nouvelle)
		\item[] Minghui Xiong (Sun Yat-sen University)
		\item[] Niki Pfeifer (Munich Center for Mathematical Philosophy)
		\item[] Patrick Bondy (Cornell University)
		\item[] Paula Olmos (Universidad Autónoma de Madrid)
		\item[] Rudi Palmieri (University of Liverpool)
		\item[] Ruth Amossy (Tel-Aviv University)
		\item[] Sara Greco (Università della Svizzera Italiana)
		\item[] Sarah Bigi (Università Cattolica del Sacro Cuore)
		\item[] Scott Aikin (Vanderbilt University)
		\item[] Steven Patterson (Marygrove College)
		\item[] Susan Kline (The Ohio State University)
		\item[] Thierry Herman (Universities of Neuchatel and lausanne)
		\item[] Yun Xie (Sun Yat-sen University)

@@
